QECO: A QoE-Oriented Computation Offloading Algorithm based on Deep Reinforcement Learning for Mobile Edge Computing

### 2024-10-08 Revision/Paper_Rev.tex
Rev_V5.4

\textcolor{blue}{To cope with the dynamic nature of the network, recent research has proposed several task offloading algorithms using machine learning methods. In particular, reinforcement learning (RL) \cite{mnih2015human} hold promises to determine optimal decision-making policies by capturing the dynamics of environments and learning strategies for accomplishing long-term objectives \cite{arulkumaran2017deep}. RL can effectively tackle the challenges of MEC arising from the ever-changing nature of networks, MDs, and servers' heterogeneity. This ultimately improves the MD users' QoE. }\\

@@

Although DRL-based methods have demonstrated their effectiveness in handling network dynamics, task offloading still encounters several challenges that require further attention.  \textcolor{blue}{As shown in Table~\ref{table1}, current research primarily focuses on minimizing energy consumption \cite{tang2022uav}, reducing processing delays \cite{guo2022energy}, \cite{seo2022differential}, maximizing computation rates~\cite{huang2019deep}, or optimizing a weighted balance among performance factors \cite{li2022joint}. However, QoE is a time-varying performance measure that reflects user satisfaction and is not affected only by delay, as considered in \cite{sun2024hierarchical}, \cite{9253665} but also by energy consumption \cite{Bolourian-WCL24}, \cite{huang2021deadline}. A more comprehensive approach is required to address the dynamic requirements of individual users in real-time scenarios with multiple MDs and ENs. 
	While some existing works such as \cite{liao2023online}, \cite{wu2024privacy}, \cite{dai2020edge}, \cite{gao2022large}, \cite{li2022joint} have investigated the trade-off between delay and energy consumption, they fail to address the user demands and fulfill QoE requirements properly.} In contrast to the aforementioned works, we propose a DRL-based distributed algorithm that provides users with an appropriate balance among QoE factors based on their demands. %We also explore a more realistic MEC scenario involving delay-sensitive tasks with processing deadlines, posing a more intricate challenge.

@@

In this study, we delve into the computation task offloading problem in MEC systems, where strict task processing deadlines and energy constraints can adversely affect the system performance. We propose a distributed QoE-oriented computation offloading (QECO) algorithm that leverages DRL to efficiently handle task offloading in uncertain loads at ENs. This algorithm empowers MDs to make offloading decisions utilizing only locally observed information, such as task size, queue details, \textcolor{blue}{energy status}, and historical workloads at the ENs. By adopting the appropriate policy based on each MD’s specific requirements at any given time, the QECO algorithm significantly improves the QoE for individual users.

@@

\newpage.\newpage

@@

In recent years, edge computing has become a popular method for scenarios that need to process massive data with weak devices, such as IoTs \cite{zhang2023multi}, Internet of Vehicles (IoVs) \cite{lin2022multi}, \cite{wei2023many}, and Industrial IoT (IIoT) \cite{yuan2023adaptive} environment. We explore state-of-the-art RL-based techniques characteristic to discuss how they address task offloading problems in MEC.

@@

	 To take advantage of RL methods for online computation offloading in MEC, Huang \textit{et al.} in \cite{huang2019deep}, focused on a wireless-powered MEC. They proposed a DRL-based approach, capable of attaining near-optimal decisions. This is achieved by selectively considering a compact subset of candidate actions in each iteration. Liu \textit{et al.} in \cite{liu2021learn} investigated a two-timescale computing offloading and resource allocation problem and proposed a resource coordination algorithm based on multi-agent DRL, which can generate interactive information along with resource decisions. Zhou \textit{et al.} in \cite{zhou2021deep} used an MDP to model the interactions of the environment. They proposed a Q-learning approach to achieve optimal resource allocation strategies and computation offloading. Liao \textit{et al.} in \cite{liao2023online} introduced a double DRL algorithm for performing online computation offloading in MEC. This algorithm optimizes transmission power and scheduling of CPU frequency when minimizing both task computation delay and energy consumption. In these researches authors investigated simple MEC networks and explored computation offloading problems, mainly focused on delay-tolerant tasks or single MEC network model. Specifically, the work \cite{huang2019deep}, \cite{liu2021learn} not consider delay-sensitive tasks for network models. In works \cite{zhou2021deep}, \cite{liao2023online}, authors just considered the situation of a single server or user in the MEC system, which may not always reflect real-world scenarios.

	 In actual scenarios, an MEC system needs to provide delay-constrained services with veraity MDs and ENs involved. A more accurate MEC model is required to address difficulties of dynamic resource scheduling in large scale scenarios. 
	 Some studies explored task offloading problems in a more advanced scenarios. Chen et al. in [5] examined a joint optimization problem of computation offloading and resource allocation to minimize the task processing delay and the energy consumption of all the MDs. Wu \textit{et al.} in \cite{wu2023computation} introduced a stochastic game-based resource allocation in the SDN-based MEC network. They used an MDP and proposed a multi-agent RL method to minimize both energy consumption and processing delay. Dai \textit{et al.} in \cite{dai2020edge} introduced the integration of action refinement into DRL and designed an algorithm to concurrently optimize resource allocation and computation offloading. 
However, these works did not take into account the challenges of dynamic network environment. For instance, in \cite{liao2023online}, MDs are assumed to have sufficient transmission and computation resources from ENs, which may not always align with real-world conditions. While the works of \cite{wu2023computation} and \cite{zhao2019deep} investigated the limited capacities MEC, they did not consider the dynamic workload at ENs in decision making prosseces, imposing significant challenges in overall system performance.

@@

@@

 To reflecting real-world scenarios more accurately, the authors applied queuing theory to model MEC systems. It helps in modeling the dynamic nature of network, allowing MEC systems to allocate computational and transmission resources more efficiently.
	In \cite{Bolourian-WCL24}, the authors proposed an offloading algorithm using deep Q-learning for wireless-powered IoT devices in MEC systems. This algorithm aims to minimize the task drop rate while the devices solely rely on harvested energy for operation. Tang \textit{et al.} in \cite{9253665} investigated the task offloading problem for indivisible and deadline-constrained computational tasks in MEC systems. The authors proposed a distributed DRL-based offloading algorithm designed to handle uncertain workload dynamics at the ENs. 
	In \cite{huang2021deadline}, Huang \textit{et al.} proposed a DRL-based method based on a partially observable MDP (POMDP), which guarantees the deadlines of real-time tasks while minimizing the total energy consumption of MDs. This algorithm effectively tackles the challenges of dynamic resource allocation in large-scale heterogeneous networks. To optimize delay and energy consumption in an MEC-based IIoT system, Wu \textit{et al.} in \cite{wu2023multi} proposed a multi-agent DQN-based method based on POMDP to address computation offloading problem. In \cite{gao2022large}, Gao \textit{et al.} introduced an attention-based multi-agent algorithm designed for decentralized computation offloading.

\subsection{Task Offloading Considering EN's Workload}

In practice, ENs may have limited processing capacities, so the processing capacity that an EN allocated to a MD depends on the workload level at the EN (i.e., number of concurrent tasks offloaded to the EN), which may cused those offloaded tasks may experience large processing delay. Some of the tasks may even be dropped when their deadlines expire. 
Some existing works have addressed the load levels at the edge nodes and proposed task offloading algorithms. 
 To optimize privacy protection and quality of service, authors in \cite{wu2024privacy} investigated the joint computation offloading and power allocation problems for the IIoT network. They modeled the problem as an MDP and proposed a multi-agent DQN-based algorithm.
In \cite{zhao2019deep}, Zhao \textit{et al.} proposed a computation offloading algorithm based on DRL, which addresses the competition for wireless channels to optimize long-term downlink utility. In this approach, each MD requires quality-of-service information from other MDs.
	 To minimize energy consumption, Munir \textit{et al.} \cite{munir2021multi} developed a semi-distributed approach using a multi-agent RL framework for self-powered MEC. Gong \textit{et al.} in \cite{gong2022edge} proposed a DRL-based network structure in the industrial IoT (IIoT) systems to jointly optimize task offloading and resource allocation to achieve lower energy consumption and decreased task delay. To investigate privacy aware computation offloading problem, Wu \textit{et al.} in \cite{wu2024combining} proposed a deep Q-network (DQN)-based method. They transform the problem on MDP to optimize computation rate and energy consumption in a queuing-based IIoT network. Sun \textit{et al.} in \cite{sun2024hierarchical} explored both computation offloading and service caching problems in MEC. They formulated an optimization problem that aims to minimize the long-term average service delay. They then proposed a hierarchical DRL framework, which effectively handles both problems under heterogeneous resources.
However, these algorithms in [6]–[9] may require global information of the system (e.g., the arrivals and the sizes of the tasks of all MDs) and may incur high signaling overhead.

@@

Although DRL-based methods have demonstrated their effectiveness in handling network dynamics, task offloading still encounters several challenges that require further attention.  As shown in Table~\ref{table1}, current research primarily focuses on minimizing energy consumption \cite{tang2022uav}, reducing processing delays \cite{guo2022energy}, \cite{seo2022differential}, maximizing computation rates~\cite{huang2019deep}, or optimizing a weighted balance among performance factors \cite{li2022joint}. However, QoE is a time-varying performance measure that reflects user satisfaction and is not affected only by delay, as considered in \cite{sun2024hierarchical}, \cite{9253665} but also by energy consumption \cite{Bolourian-WCL24}, \cite{huang2021deadline}. A more comprehensive approach is required to address the dynamic requirements of individual users in real-time scenarios with multiple MDs and ENs. 
	While some existing works such as \cite{liao2023online}, \cite{wu2024privacy}, \cite{dai2020edge}, \cite{gao2022large}, \cite{li2022joint} have investigated the trade-off between delay and energy consumption, they fail to address the user demands and fulfill QoE requirements properly. In contrast to the aforementioned works, we propose a DRL-based distributed algorithm that provides users with an appropriate balance among QoE factors based on their demands.

@@

\newpage

@@

\begin{table*}[htbp]\textcolor{blue}{
		\renewcommand{\arraystretch}{0.7}
		\captionsetup{name=TABLE}
		\caption{Comparison of Related Works Characteristic}
		\scalebox{1}{%
			\begin{tabular}{ lp{2.2cm}p{3cm}p{3.4cm}p{0.7cm}p{2cm}p{3.2cm}l} 
				\toprule
				\textbf{Paper} & \textbf{Scenario} &  \textbf{Problem} &  \textbf{Objective} &  \textbf{Model} & \textbf{Method} &  \textbf{Drawbacks}  \\ \midrule
				\cite{liao2023online} & Queuing-based MEC & Online computation offloading & Minimize computation delay and energy consumption & MDP & DDPG + DDQN & Only for a singel MEC system model  \\\midrule
				\cite{zhou2021deep} & heterogeneous MEC & Resource allocation and computation offloading & Minimize energy consumption of the entire system & MDP & DDQN & Only for a singel MEC system model \\\midrule				
				\cite{huang2019deep} & Wireless-powered MEC & Computation offloading and resource allocations & Maximize computation rate & MIP & DQN & Not consider delay-sensitive tasks \\\midrule
				\cite{wu2024privacy} & MEC-based IIoT  & Joint power allocation and computation offloading  & Optimization of privacy protection and quality of service. & MDP & Multi-agent actor-critic network& Not take user's demand into consideration \\\midrule
				\cite{zhao2019deep} & MEC & User association and resource allocation & Optimize downlink utility & MDP & Multi-agent D3QN & Not consider system delay and energy consumtion \\\midrule
				\cite{sun2024hierarchical} & MEC & Computation offloading and service caching & Minimize average service delay & MDP & hierarchical DRL & Not consider system energy consumtion \\\midrule
				\cite{wu2023computation} & SDN-based MEC & Stochastic game-based resource allocation & Minimize energy consumption and processing delay & MDP & Multi-agent RL & Not consider tasks with maximum delay tolerance\\\midrule
				\cite{dai2020edge} & MEC & Resource allocation and computation offloading & Minimize energy consumption & MDP & DDPG & Not take user's demand into consideration \\\midrule
				\cite{liu2021learn} & MEC & Resource allocation and computation offloading & Minimize execution cost & POMDP & Multi-agent actor-critic network &  Not consider delay-sensitive tasks \\\midrule
				\cite{gong2022edge} & MEC-based IIoT & Resource allocation and computation offloading & Minimize task computation delay and energy consumption & MDP & DRL & Not take user's demand into consideration\\\midrule
				\cite{gao2022large} & Queuing-based heterogeneous MEC & Decentralized computation offloading & Optimize system cost and completion rates & MDP & Multi-agent actor-critic network& Not take user's demand into consideration \\\midrule
				\cite{9253665} &  Queuing-based MEC &  Computation offloading & Minimize drop rate and computation delay. & MDP & D3QN + LSTM & Not consider system energy consumtion\\\midrule
				\cite{wu2024combining} & Queuing-based IIoT MEC & Privacy aware computation offloading & Optimization of computation rate and energy consumption & MDP & Actor-critic network  & Not take user's demand into consideration \\\midrule
				\cite{wu2023multi} & Queuing-based IIoT MEC & Computation offloading & Optimize delay and energy consumption & POMDP & Multi-agent DQN&  Not consider tasks with maximum delay tolerance \\\midrule
				\cite{huang2021deadline} & Queuing-based MEC & Computation offloading & Optimize drop rate and energy consumption & POMDP & DDPG & Not consider computation delay \\ \midrule
				\cite{Bolourian-WCL24} & Queuing-based MEC with EHs& Energy harvesting  computation offloading & Minimize drop rate and energy consumption. & MDP  & DQN & Not consider computation delay  \\\midrule
				QECO &  Queuing-based MEC &  Computation offloading & Maximize the QoE of each MD individually &MDP & D3QN + LSTM & \\
				\toprule
		\end{tabular}}
		\label{table1}}
\end{table*}

>>>>

@@

To cope with the dynamic nature of the network, recent research has proposed several task offloading algorithms using machine learning methods. In particular, reinforcement learning (RL) \cite{mnih2015human} hold promises to determine optimal decision-making policies by capturing the dynamics of environments and learning strategies for accomplishing long-term objectives. RL can effectively tackle the challenges of MEC arising from the ever-changing nature of networks, MDs, and servers' heterogeneity, ultimately improving the MD users’ QoE. 
While DRL-based methods have demonstrated their effectiveness in handling network dynamics, task offloading still encounters several challenges that require further attention. However, QoE is a time-varying performance measure that reflects user satisfaction and is not affected only by delay \cite{guo2022energy}, but also by energy consumption \cite{tang2022uav}. Albeit some existing works have investigated the trade-off between delay and energy consumption \cite{li2022joint}, they fail to properly address the user demands and fulfill QoE requirements. A more comprehensive approach is required to address the dynamic requirements of individual users in real-time scenarios with multiple MDs and ENs.

In this study, we delve into the computation task offloading problem in MEC systems, where strict task processing deadlines and energy constraints can adversely affect the system's performance. To mitigate these challenges, we propose a distributed QoE-oriented computation offloading (QECO) algorithm, leveraging DRL to enhance decision-making in real-time and uncertain environments. Unlike conventional approaches that require global information, QECO allows MDs to make offloading decisions and select the most suitable EN based on locally available data, including task size, queue status, energy levels, and the historical workload of ENs. Specifically, QECO integrates predictive models to continuously estimate dynamic workloads at ENs, enabling MDs to proactively adjust their offloading strategies in real time, even under high network volatility. With a focus on task completion, delay, and energy consumption, QECO quantifies the QoE for MDs and strikes an optimal balance among these factors. By adopting the appropriate policy based on each MD’s specific requirements at any given time, the QECO algorithm significantly improves the QoE for individual users.

%In this respect, we model the problem by introducing queuing theory in a dynamic MEC environment, so that our work will be closer to real conditions and easier to apply in practice.

%In contrast to the aforementioned works [9]–[20], we propose a DRL-based distributed algorithm that provides users with an appropriate balance among QoE factors based on their demands. We also explore a more realistic MEC scenario involving delay-sensitive tasks with processing deadlines, posing a more intricate challenge.

%While DRL-based methods DRL-based methods have demonstrated their effectiveness in handling network dynamics, task offloading still encounters several challenges that require further attention. Current research primarily focuses on minimizing energy consumption, reducing processing delays, maximizing computation rates, or optimizing a weighted balance among performance factors. However, QoE is a time-varying performance measure that reflects user satisfaction and is not affected only by delay, but also by energy consumption. A more comprehensive approach is required to address the dynamic requirements of individual users in real-time scenarios with multiple MDs and ENs. While some existing works have investigated the trade-off between delay and energy consumption, they fail to address the user demands and fulfill QoE requirements properly.

% In contrast to the aforementioned works, we propose a DRL-based distributed algorithm that provides users with an appropriate balance among QoE factors based on their demands. %We also explore a more realistic MEC scenario involving delay-sensitive tasks with processing deadlines, posing a more intricate challenge.

@@

%In this study, we delve into the computation task offloading problem in MEC systems, where strict task processing deadlines and energy constraints can adversely affect the system performance. We propose a distributed QoE-oriented computation offloading (QECO) algorithm, which empowers MDs to make offloading decisions and selecting appropriot EN utilizing only locally observed information, such as task size, queue details, energy status, and historical workloads at the ENs. Speaceficlly, by estimating the EN's dynamic workload, QECO efficiently handle task offloading in uncertain MEC environment, lead to improving overal system performance. By adopting the appropriate policy based on each MD’s specific requirements at any given time, the QECO algorithm significantly improves the QoE for individual users.

@@

@@

In recent years, edge computing has become a popular method for scenarios that need to process massive data with weak devices, such as IoTs \cite{zhang2023multi}, Internet of Vehicles (IoVs) \cite{lin2022multi}, \cite{wei2023many}, and Industrial IoT (IIoT) \cite{yuan2023adaptive} environment, while uncertain requirements and sensitive latency properties of computation tasks pose nontrivial challenges in MEC systems with limited resources. To cope with the dynamic nature of the network, recent research has proposed several task offloading algorithms using machine learning methods. In particular, reinforcement learning (RL) \cite{mnih2015human} hold promises to determine optimal decision-making policies by capturing the dynamics of environments and learning strategies for accomplishing long-term objectives \cite{arulkumaran2017deep}. RL can effectively tackle the challenges of MEC arising from the ever-changing nature of networks, MDs, and servers' heterogeneity. This ultimately improves the MD users' QoE. 
We explore state-of-the-art RL-based techniques characteristic to discuss how they address task offloading problems in MEC. Table~\ref{table1} provides an intuitive comparison of the related works.

@@

	 To take advantage of RL methods for online computation offloading in MEC, Huang \textit{et al.} in \cite{huang2019deep}, focused on a wireless-powered MEC. They proposed a DRL-based approach, capable of attaining near-optimal decisions. This is achieved by selectively considering a compact subset of candidate actions in each iteration. Liu \textit{et al.} in \cite{liu2021learn} investigated a two-timescale computing offloading and resource allocation problem and proposed a resource coordination algorithm based on multi-agent DRL, which can generate interactive information along with resource decisions. 
	 Zhou \textit{et al.} in \cite{zhou2021deep} used an MDP to model the interactions of the environment. They proposed a Q-learning approach to achieve optimal resource allocation strategies and computation offloading. 
	 Wu \textit{et al.} in \cite{wu2023computation} introduced a stochastic game-based resource allocation in the SDN-based MEC network. They used an MDP and proposed a multi-agent RL method to minimize both energy consumption and processing delay.
	 In these researches authors investigated simple MEC networks and explored computation offloading problems, mainly focused on delay-tolerant tasks or single MEC network model. Specifically, the work \cite{huang2019deep}, \cite{liu2021learn}, \cite{wu2023computation} not consider delay-sensitive tasks for network models. 
	 In works \cite{zhou2021deep}, \cite{liao2023online}, \cite{wu2023computation} authors just considered the situation of a single server or user in the MEC system, which may not always reflect real-world scenarios.
	 In actual scenarios, an MEC system needs to provide delay-constrained services with veraity MDs and ENs involved. A more accurate MEC model is required to address difficulties of dynamic resource scheduling in large scale scenarios.

	 Some studies explored task offloading problems in a more advanced scenarios.  To optimize privacy protection and quality of service, authors in \cite{wu2024privacy} investigated the joint computation offloading and power allocation problems for the IIoT network. They modeled the problem as an MDP and proposed a multi-agent DQN-based algorithm.
	 Chen et al. in [5] examined a joint optimization problem of computation offloading and resource allocation to minimize the task processing delay and the energy consumption of all the MDs.  Dai \textit{et al.} in \cite{dai2020edge} introduced the integration of action refinement into DRL and designed an algorithm to concurrently optimize resource allocation and computation offloading.
	 In \cite{zhao2019deep}, Zhao \textit{et al.} proposed a computation offloading algorithm based on DRL, which addresses the competition for wireless channels to optimize long-term downlink utility. In this approach, each MD requires quality-of-service information from other MDs. 
However, these works did not take into account the challenges of dynamic network environment. For instance, in \cite{}, MDs are assumed to have sufficient transmission and computation resources from ENs, which may not always align with real-world conditions. While the works of \cite{wu2023computation} and \cite{zhao2019deep} investigated the limited capacities MEC, they did not consider the dynamic workload at ENs in decision making prosseces, imposing significant challenges in overall system performance.

@@

\begin{table*}[htbp]\textcolor{blue}{
		\renewcommand{\arraystretch}{0.7}
		\captionsetup{name=TABLE}
		\caption{Comparison of Related Works Characteristic}
		\scalebox{1}{%
			\begin{tabular}{ lp{2.2cm}p{3cm}p{3.4cm}p{0.7cm}p{2cm}p{3.2cm}l} 
				\toprule
				\textbf{Paper} & \textbf{Scenario} &  \textbf{Problem} &  \textbf{Objective} &  \textbf{Model} & \textbf{Method} &  \textbf{Drawbacks}  \\ \midrule
				\cite{liao2023online} & Queuing-based MEC & Online computation offloading & Minimize computation delay and energy consumption & MDP & DDPG + DDQN & Only for a singel MEC system model  \\\midrule
				\cite{zhou2021deep} & heterogeneous MEC & Resource allocation and computation offloading & Minimize energy consumption of the entire system & MDP & DDQN & Only for a singel MEC system model \\\midrule				
				\cite{huang2019deep} & Wireless-powered MEC & Computation offloading and resource allocations & Maximize computation rate & MIP & DQN & Not consider delay-sensitive tasks \\\midrule
				\cite{wu2024privacy} 2& MEC-based IIoT  & Joint power allocation and computation offloading  & Optimization of privacy protection and quality of service. & MDP & Multi-agent actor-critic network& Not take user's demand into consideration \\\midrule
				\cite{zhao2019deep} & MEC & User association and resource allocation & Optimize downlink utility & MDP & Multi-agent D3QN & Not consider system delay and energy consumtion \\\midrule
				\cite{sun2024hierarchical} & MEC & Computation offloading and service caching & Minimize average service delay & MDP & hierarchical DRL & Not consider system energy consumtion \\\midrule
				\cite{wu2023computation} 1 & SDN-based MEC & Stochastic game-based resource allocation & Minimize energy consumption and processing delay & MDP & Multi-agent RL & Not consider tasks with maximum delay tolerance\\\midrule
				\cite{dai2020edge} & MEC & Resource allocation and computation offloading & Minimize energy consumption & MDP & DDPG & Not take user's demand into consideration \\\midrule
				\cite{liu2021learn} & MEC & Resource allocation and computation offloading & Minimize execution cost & POMDP & Multi-agent actor-critic network &  Not consider delay-sensitive tasks \\\midrule
				\cite{gong2022edge} & MEC-based IIoT & Resource allocation and computation offloading & Minimize task computation delay and energy consumption & MDP & DRL & Not take user's demand into consideration\\\midrule
				\cite{gao2022large} + & Queuing-based heterogeneous MEC & Decentralized computation offloading & Optimize system cost and completion rates & MDP & Multi-agent actor-critic network& Not take user's demand into consideration \\\midrule
				\cite{9253665} + &  Queuing-based MEC &  Computation offloading & Minimize drop rate and computation delay. & MDP & D3QN + LSTM & Not consider system energy consumtion\\\midrule
				\cite{wu2024combining} 1 & Queuing-based IIoT MEC & Privacy aware computation offloading & Optimization of computation rate and energy consumption & MDP & Actor-critic network  & Not take user's demand into consideration \\\midrule
				\cite{wu2023multi} 1& Queuing-based IIoT MEC & Computation offloading & Optimize delay and energy consumption & POMDP & Multi-agent DQN&  Not consider tasks with maximum delay tolerance \\\midrule
				\cite{huang2021deadline} & Queuing-based MEC & Computation offloading & Optimize drop rate and energy consumption & POMDP & DDPG & Not consider computation delay \\ \midrule
				\cite{Bolourian-WCL24} - & Queuing-based MEC with EHs& Energy harvesting  computation offloading & Minimize drop rate and energy consumption. & MDP  & DQN & Not consider computation delay  \\\midrule
				QECO &  Queuing-based MEC &  Computation offloading & Maximize the QoE of each MD individually &MDP & D3QN + LSTM & \\
				\toprule
		\end{tabular}}
		\label{table1}}
\end{table*}

@@

 To reflecting real-world scenarios more accurately, the authors applied queuing theory to model MEC systems. It helps in modeling the dynamic nature of network, allowing MEC systems to allocate computational and transmission resources more efficiently.
To investigate privacy aware computation offloading problem, Wu \textit{et al.} in \cite{wu2024combining} proposed a deep Q-network (DQN)-based method. They transform the problem on MDP to optimize computation rate and energy consumption in a queuing-based IIoT network.
Liao \textit{et al.} in \cite{liao2023online} introduced a double DRL algorithm for performing online computation offloading in MEC. This algorithm optimizes transmission power and scheduling of CPU frequency when minimizing both task computation delay and energy consumption. 
	In \cite{Bolourian-WCL24}, the authors proposed an offloading algorithm using deep Q-learning for wireless-powered IoT devices in MEC systems. This algorithm aims to minimize the task drop rate while the devices solely rely on harvested energy for operation. 
	In \cite{huang2021deadline}, Huang \textit{et al.} proposed a DRL-based method based on a partially observable MDP (POMDP), which guarantees the deadlines of real-time tasks while minimizing the total energy consumption of MDs. This algorithm effectively tackles the challenges of dynamic resource allocation in large-scale heterogeneous networks.
	To minimize energy consumption, Munir \textit{et al.} \cite{munir2021multi} developed a semi-distributed approach using a multi-agent RL framework for self-powered MEC.

\subsection{Task Offloading Considering EN's Workload}
In practice, ENs may have limited processing capacities, so the processing capacity that an EN allocated to a MD depends on the workload level at the EN (i.e., number of concurrent tasks offloaded to the EN), which may cused those offloaded tasks may experience large processing delay. Some of the tasks may even be dropped when their deadlines expire. 
Some existing works have addressed the load levels at the edge nodes and proposed task offloading algorithms. 
To optimize delay and energy consumption in an MEC-based IIoT system, Wu \textit{et al.} in \cite{wu2023multi} proposed a multi-agent DQN-based method based on POMDP to address computation offloading problem.
Tang \textit{et al.} in \cite{9253665} investigated the task offloading problem for indivisible and deadline-constrained computational tasks in MEC systems. The authors proposed a distributed DRL-based offloading algorithm designed to handle uncertain workload dynamics at the ENs. 
 In \cite{gao2022large}, Gao \textit{et al.} introduced an attention-based multi-agent algorithm designed for decentralized computation offloading.
	 Gong \textit{et al.} in \cite{gong2022edge} proposed a DRL-based network structure in the industrial IoT (IIoT) systems to jointly optimize task offloading and resource allocation to achieve lower energy consumption and decreased task delay. Sun \textit{et al.} in \cite{sun2024hierarchical} explored both computation offloading and service caching problems in MEC. They formulated an optimization problem that aims to minimize the long-term average service delay. They then proposed a hierarchical DRL framework, which effectively handles both problems under heterogeneous resources.
However, these algorithms in [6]–[9] may require global information of the system (e.g., the arrivals and the sizes of the tasks of all MDs) and may incur high signaling overhead.

@@

%Although DRL-based methods have demonstrated their effectiveness in handling network dynamics, task offloading still encounters several challenges that require further attention.  As shown in Table~\ref{table1}, current research primarily focuses on minimizing energy consumption \cite{tang2022uav}, reducing processing delays \cite{guo2022energy}, \cite{seo2022differential}, maximizing computation rates~\cite{huang2019deep}, or optimizing a weighted balance among performance factors \cite{li2022joint}. However, QoE is a time-varying performance measure that reflects user satisfaction and is not affected only by delay, as considered in \cite{sun2024hierarchical}, \cite{9253665} but also by energy consumption \cite{Bolourian-WCL24}, \cite{huang2021deadline}. A more comprehensive approach is required to address the dynamic requirements of individual users in real-time scenarios with multiple MDs and ENs. While some existing works such as \cite{liao2023online}, \cite{wu2024privacy}, \cite{dai2020edge}, \cite{gao2022large}, \cite{li2022joint} have investigated the trade-off between delay and energy consumption, they fail to address the user demands and fulfill QoE requirements properly. In contrast to the aforementioned works, we propose a DRL-based distributed algorithm that provides users with an appropriate balance among QoE factors based on their demands.

@@

@@
